Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-07 paper/paper.tex
Small changes to methods made before recent comments, will continue to update!

\subsection{IFN reporter cell lines}
\jdbcomment{Alistair writes this}
For our type I interferon reporters, A 1kb region upstream of the human IFNB1 gene was cloned into the pHAGE2 lentiviral vector, with a NotI site immediately downstream serving as an artificial Kozak sequence (REF). 
Downstream of this NotI site, each of the following reporter constructs was cloned: mCherry, mNeongreen, and mNeongreen translationally linked to LNGFR$\delta$C by a p2A linker (REFS).
For our type III interferon reporters, a 1.2kb region upstream of the human IL29 (IFNL1) gene was cloned into the pHAGE2 vector, with the native kozak sequence left at the 3' end. 
Downstream of this promoter zsGreen translationally linked to LNGFR$\delta$C via a p2A linker was cloned. 
Replication-incompetent lentivirus was generated from these vectors as previously described (REF).
A monolayer of A549 cells in D10 was transduced with each lentivirus in the presence of 5 $\mu$g polybrene, and sorted as single cells. 
These single cell clones were grown and tested for reporter activity by poly I:C transfection---a potent agonist of the RIG-I pathway.
Critically, cells propagated and used in experiments were not exposed to poly I:C,  thus avoiding selection on survival post interferon-induction.
For our dual- type I and type III reporter, a single-cell clone of our type III reporter strain was transduced with our type I reporter bearing the mCherry fluorescent marker and subsequently propagated as a single cell clone and validated as above.

@@

\subsection{Viral stocks}
\jdbcomment{Alistair writes this}
All viruses were generated using reverse-genetics as previously described.
Briefly, bidirectional plasmids producing viral mRNA and vRNA are transfected into a co-culture of MDCK-SIAT1 and 293t cells grown in D10.
After 24h, media is changed from D10 to influenza growth media.
Between 48h and 72h post-infection, depending on viral growth kinetics, supernatant was harvested and titered by TCID50.
Virus was subsequently expanded on MDCK-SIAT1 cells as described below.
For all viral variants, the described mutations were introduced into reverse-genetics plasmids using PCR mutagenesis. 
For the HA-flanked mCherry pseudovirus, a plasmid was generated similarly to a previously-described HA-flanked eGFP vector.
Synonymously-barcoded virus utilized previously described 3' synonymous mutations, and two newly-introduced single-nucleotide synonymous mutations at the 5' end of each viral gene.
Wild-type, synonymously-barcoded, NS1-inactivated, and single-nucleotide variant viruses were all grown in unmodified MDCK-SIAT1 and 293t cells.
Viral variants bearing large internal deleltions in the PB1 segment were grown in MDCK-SIAT1 and 293t cells expressing PB1 as previously described.
Pseudovirus expressing mCherry in place of eGFP was grown in MDCK-SIAT1 and 293t cells expressing HA as previously described.

@@

\subsection{Single-cell infections and transcriptomics using 10X Chromium on IFN-enriched cells}
\jdbcomment{Alistair writes this}

\subsection{Enrichment and preparation of viral cDNA for PacBio sequencing}
\jdbcomment{Alistair writes this}

>>>>

\subsection{IFN reporter cell lines}
\jdbcomment{Alistair writes this}
For our type I interferon reporters, A 1kb region upstream of the human IFNB1 gene was cloned into the pHAGE2 lentiviral vector, with a NotI site immediately downstream serving as an artificial Kozak sequence (REF). 
Downstream of this NotI site, each of the following reporter constructs was cloned: mCherry, mNeongreen, and mNeongreen translationally linked to low-affinity nerve growth factor lacking the C-terminal signaling domain (LNGFR$\Delta$C) by a p2A linker (REFS).
For our type III interferon reporters, a 1.2kb region upstream of the human IL29 (IFNL1) gene was cloned into the pHAGE2 vector, with the native kozak sequence left at the 3' end. 
Downstream of this promoter zsGreen translationally linked to LNGFR$\Delta$C via a p2A linker was cloned. 
Replication-incompetent lentivirus was generated from these vectors as previously described (REF).
A monolayer of A549 cells in D10 was transduced with each lentivirus in the presence of 5 $\mu$g polybrene, and sorted as single cells. 
These single cell clones were grown and tested for reporter activity by poly I:C transfection---a potent agonist of the RIG-I pathway.
Critically, cells propagated and used in experiments were not exposed to poly I:C,  thus avoiding selection on survival post interferon-induction.
For our dual- type I and type III reporter, a single-cell clone of our type III reporter strain was transduced with our type I reporter bearing the mCherry fluorescent marker and subsequently propagated as a single cell clone and validated as above.

@@

\subsection{Viral stocks}
\jdbcomment{Alistair writes this}
All viruses were generated using reverse-genetics as previously described.
All infections were performed in influenza growth media as previously described.
Briefly, bidirectional plasmids producing viral mRNA and vRNA are transfected into a co-culture of MDCK-SIAT1 and 293t cells grown in D10.
After 24h, media is changed from D10 to influenza growth media.
Between 48h and 72h post-infection, depending on viral growth kinetics, supernatant was harvested and titered by TCID50.
Virus was subsequently expanded on MDCK-SIAT1 cells as described below.
For all viral variants, the described mutations were introduced into reverse-genetics plasmids using PCR mutagenesis. 
For the HA-flanked mCherry pseudovirus, a plasmid was generated similarly to a previously-described HA-flanked eGFP vector.
Synonymously-barcoded virus utilized previously described 3' synonymous mutations, and two newly-introduced single-nucleotide synonymous mutations at the 5' end of each viral gene.
Wild-type, synonymously-barcoded, NS1-inactivated, and single-nucleotide variant viruses were all grown in unmodified MDCK-SIAT1 and 293t cells.
Viral variants bearing large internal deleltions in the PB1 segment were grown in MDCK-SIAT1 and 293t cells expressing PB1 as previously described.
Pseudovirus expressing mCherry in place of eGFP was grown in MDCK-SIAT1 and 293t cells expressing HA as previously described.

@@

\subsection{Single-cell infections and transcriptomics using 10X Chromium on IFN-enriched cells}
Type I interferon reporter A549 cells (mNeongreen-p2A-LNGFR$/Delta$C) were infected with a mixture of barcoded (MOI 0.1) and wild-type (MOI 0.02) virus. 
These differing MOI's were chosen to roughly match the fraction of HA-positive cells in flow cytometry experiments (and thus biologically active particles) titering these two stocks. 
Infections were allowed to proceed for 12h.
Cells were trypsonized, trypsin was quenched with D10 media, and cells were resuspended in de-gassed PBS supplemented with 0.5\% bovine serum albumin and 5 mM EDTA. 
Cells were then incubated with anti-LNGFR MACSelect Microbeads and passed over an MS magnetic column twice, selecting the positive population each time. The original, unsorted, population was then added back in to approximately 10 percent of the final cell fraction in order to ensure the presence of interferon negative cells. 
At this point, uninfected MDCK-SIAT1 cells were also added to approximately 10 percent of the final cell fraction for doublet and lysis metrics. 
The final cell suspension was counted using a disposable hemocytometer and loaded on the 10x Genomics instrument at a targeted capture of ~1500 cells.

This sample was then processed according to the manufacturer's protocol using the Chromium Single Cell 3? Library and Gel Bead Kit v2 with one important modification; rather than process all full-length cDNA through enzymatic fragmentation, several nanograms were retained for targeted sequencing as described below.

\jdbcomment{Alistair writes this}

\subsection{Enrichment and preparation of viral cDNA for PacBio sequencing}
Approximately 1ng of full-length 10x-barcoded cDNA was used as template in an emulsion PCR using the

\jdbcomment{Alistair writes this}
